Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-01-26 paper.tex
changes int section 1 and the beginning of section 2

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The dependency on the correct functioning of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control, health care, surveillance, mobile devices, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory, in order to meet increasing computational power demands. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation. However, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, and supporting new software architectures and legacy designs (usually written in low-level languages). The present research discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of micro-grids and cyber-physical systems, are then considered, as a prominent verification and synthesis application for achieving a \textit{correct-by-construction} design.
\end{abstract}

@@

Generally, embedded computer systems perform dedicated functions with a high degree of reliability. They are used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers~\cite{Kopetz11}. Embedded systems are ubiquitous in modern day information systems, and are also becoming increasingly important in our society, especially in micro-grids, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}, and in cyber-physical systems (CPS), which demand short development cycles and again a high-level of reliability~\cite{leeCPS,leeCPS2}. As a consequence, human life has also become more and more dependent on the services provided by this type of system and, in particular, their success is strictly related to both service relevance and quality.

@@

Besides, when physical interaction with the real world is needed, which happens in CPS, additional care must be taken, mainly when human action is directly replaced, as in vehicle driving. Regarding the latter, even human-in-the-loop feedback control can be employed \cite{munir}, which then raises deeper concerns related to the reliability of human behavior modeling and system implementation. Consequently, it is important to go beyond design correctness and also address behavior correctness, which may be performed by incorporating system models. In particular, these models can be used to synthesize a given particular system, ensuring that all needed functions are correctly implemented and the correct behavior exhibited, {i.e.}, the system is indeed correct by its method of construction~\cite{Abate17}.

@@

We cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, and counter-example guided inductive synthesis in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, we describe the main challenges regarding the verification and synthesis of embedded systems, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research. Section~\ref{achievements} describes current achievements and future trends in verification and synthesis of embedded systems, while we conclude and describe future work in Section~\ref{conclusions}.

@@

Bounded Model Checking (BMC) based on Boolean Satisfiability (SAT) was originally proposed to verify hardware designs~\cite{Biere99,handbook09}. Indeed, Biere {\it et al.} were able to successfully verify large digital circuits with approximately $9510$ latches and $9499$ inputs, leading to BMC formulae with $4 \times 10^6$ variables and $1.2 \times 10^7$ clauses to be checked by a standard SAT solver. BMC based on Satisfiability Modulo Theories (SMT)~\cite{BarrettSST09}, in turn, was originally proposed to deal with increasing software verification complexity~\cite{Armando06}.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The dependency on the correct functioning of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control, health care, surveillance, mobile devices, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory and sophisticated software modules, in order to meet increasing computational power demands. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation. Nonetheless, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, validating operation logic, and supporting new software architectures and legacy designs (usually written in low-level languages). The present research discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of micro-grids and cyber-physical systems, are then considered, as a prominent verification and synthesis application for achieving a \textit{correct-by-construction} design.
\end{abstract}

@@

Generally, embedded computer systems perform dedicated functions with a high degree of reliability. They are used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers~\cite{Kopetz11}. Embedded systems are ubiquitous in modern day information systems and are also becoming increasingly important in our society, especially in micro-grids, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}, in multipurpose mobile devices, which now help in performing many routine daily tasks, and in cyber-physical systems (CPS), which demand short development cycles and again high levels of reliability~\cite{leeCPS,leeCPS2}. As a consequence, human life has also become more and more dependent on services provided by this type of system and, in particular, their success is strictly related to both service relevance and quality/reliability.

@@

Besides, when physical interaction with the real world is needed, which happens in CPS, additional care must be taken, mainly when human action is directly replaced, as in vehicle driving. Regarding the latter, even human-in-the-loop feedback control can be employed \cite{munir}, which then raises deeper concerns related to the reliability of human behavior modeling and system implementation. Consequently, it is important to go beyond design correctness and also address behavior correctness, which may be performed by incorporating system models. Specifically, these models can be used to synthesize a given particular system, ensuring that all needed functions are correctly implemented and the correct behavior exhibited, {i.e.}, the system is indeed correct by its method of construction~\cite{Abate17}.

@@

We cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, and counter-example guided inductive synthesis, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, we describe the main challenges regarding the verification and synthesis of embedded systems, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research and Section \ref{Newapp} tackles new applications. Section~\ref{achievements} describes current achievements and future trends in verification and synthesis of embedded systems, while we conclude and describe future work in Section~\ref{conclusions}.

@@

Bounded Model Checking (BMC) based on Boolean Satisfiability (SAT) was originally proposed to verify hardware designs~\cite{Biere99,handbook09}. Indeed, Biere {\it et al.} were able to successfully verify large digital circuits with approximately $9510$ latches and $9499$ inputs, leading to BMC formulae with $4 \times 10^6$ variables and $1.2 \times 10^7$ clauses to be checked by standard SAT solvers. BMC based on Satisfiability Modulo Theories (SMT)~\cite{BarrettSST09}, in turn, was originally proposed to deal with increasing software verification complexity~\cite{Armando06}.
